Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-28 wpe.tex
added haven paragraph

>>>>

As a final note: there has been prior work under a similar title to
ours~\cite{haven}, but there are only superficial similarities between
the two research projects.  Haven {\sl et al.} utilize the relative
entropy to study how well small ensembles predict the distribution of
future states of dynamical (and potentially chaotic) systems.  Our
work quantifies the predictability of a single observed time series
using weighted permutation entropy and makes no assumptions about the
underlying dynamics.  {\color{red}[[Why is WPE better than relative
      entropy?]]}.
